Fourmile_inputs

### 2022-10-18 fourmile_inputs.Rmd
added prism rh

>>>>

#need to do RH!!!
#RH: =100*(EXP((17.625*TD)/(243.04+TD))/EXP((17.625*T)/(243.04+T)))
#pull in all filenames with csv
filenames <- list.files('.', pattern='.csv', full.names=F)

prismt <- list(t2010,t2011,t2012,t2013,t2014,t2015,t2016,t2017,t2018,t2019,t2020)

rh <- bind_rows(prismt) %>%
  na.omit() %>% 
  rename(tmean_c = 6, 
         tdew_c = 7) %>%
  arrange(Date) %>%
  group_by(Name, Date) %>%
  mutate(rh = 100*(exp((17.625*tdew_c)/(243.04+tdew_c))/exp((17.625*tmean_c)/(243.04+tmean_c)))) %>%
  dplyr::select(c(Date, Name, rh)) %>%
  pivot_wider(names_from = Name, values_from = rh)

write.csv(rh, 'rh.csv')
